\section{Introduction} 
\label{sec:intro}


Due to the fact that the game industry has been growing over the past years~\cite{gartner}
constructing good game \ac{AI} is becoming increasingly important.
Commonly a game \ac{AI} is created for one specific game. If humans play against
enemies, there are often varying degrees of difficulty that can be adjusted, such as easy, medium and hard.
Our aim of the course "Computational Intelligence in Games"~\footnote{http://is.cs.ovgu.de/Courses/Team+Projects/Computational+Intelligence+in+Games.html} at the Otto-von-Guericke-University Magdeburg in Germany~\footnote{http://www.ovgu.de/} has 
been the evaluation of three different approaches to the General Video Game AI Competition~\footnote{http://www.gvgai.net/}.
The game AI is supposed to play unknown games as effectively as possible. The agent can observe the
whole grid with game objects that are moving and gets information of all the collisions that are happening.
For each gamestep, the agent has 40 ms to return an action. All actions - depending on the game - are  LEFT, UP, RIGHT, DOWN, USE and NIL.
In order to find the best action, the agent can simulate steps to predict the next state. However, there is uncertainty because the game objects move randomly.

All these facts form a complex problem to solve. To win most of the games as fast as possible, he should play tight. 
Before each of the games start the aim of the controller is unknown. The agent should therefore try to dynamically find out what the goal of the current game is.

In this paper are going to introduce three general approaches for a game \ac{AI}. We will first outline our literary review and will then go on to explain the background. The theory could not always be implemented like it was proposed to, because it is necessary for it to fit the requirements of the games. For this reason we will further explain the details of our implementation in chapter four.
We will then evaluate the best parameters of each approach an finally reason which agent we consider best.








