\section{Literature Review} \label{sec:lit}
\todo{
Perform a literature review: What has been done before in this field? What is the main technique/s used in the paper, and what has it/they been used for in the literature before? Give references to the most relevant work published. Example: ~\cite{BrowneMCTSurvey}.
}

The field of \ac{CIG} is very wide and there is a lot of work related  to this theme. We are dealing with \ac{GVGP}, which belongs to the topic \ac{CIG}. 
An essential work from T. Schaul~\cite{schaul2013pyvgdl} shows how our game-environment is build-up. He describes a general video game language in which games can be described in an easy way without the knowledge of programming games. Different objects can be created and rules can be defined which decide what happens if one object collides with another. It was created for research in \ac{AI} in games. The agent which plays the game gets information (observation) about the actual state and can chose an available action. In our case, the agent gets a global observation about the game and not only a local one (e.g. first-person view). The games in this competition were created with this language to have a good basis for our algortihms.
There are several conferences which deal with the topic of \ac{CIG} e.g. the IEEE Conference on Computational Intelligence and Games (CIG) or the AAAI Conference on Artificial Intelligence and Interactive Digital Entertainment (AIIDE). The field of \ac{CIG} is very wide and contains a lot of different research areas beside \ac{GVGP} and agent decision making. Yannakakis, G.N. and Togelius, J. point out 10 main research areas of \ac{CIG}: "NPC behavior learning, search and planning, player modeling, games as AI benchmarks, procedural content generation, computational narrative, believable agents, AI-assisted game design, general game artificial intelligence and AI in commercial games"

\todo{paperbibtex suchen A Panorama of Artificial and Computational Intelligence in Games,}

This shows the variety of this research field. In the topic of \ac{GVGP} often \ac{MCTS} is used. The comprehensive description of \ac{MCTS} methods 

\todo{paperbibtex suchen a survey of monte carlo tree search methods}

describes nearly all approaches for \ac{GVGP}. 