\section{Techniques Implemented} \label{sec:exp}

Describe the controllers you created. Explain how they work, in which techniques are they based on (probably from previous section), and include figures and pseudocode as needed.


\subsection{Stay Alive} 

pessimistic iteration

grid search



\subsection{Heuristic based} 
 



\subsection{MCTS Tree} 

\begin{itemize}
  \item act choosig -> most visited node
  \item tree policy
  \item default policy
\end{itemize}



\subsection{Evolutionary algorithm} 

\begin{itemize}
  \item basics mutation score crossover
  \item sliding window
  \item adaptive path length
  \item heuristic switch
\end{itemize}
  
\subsection{Game Detection} 
  
  Another technique we have implemented is a detection of a known game. We know the 10 games from the test-set and the 10 games from the validation-set, the 10 test-set games are unknown. The Goal of the Gamedetection is to improve the score and the number of wins in the two known game-sets without decreasing the score and the number of wins in the unknown test-set. To do that, the standard parameters of the Algorithm are used when no game is detected, otherwise the optimal parameters for this game are used. These parameters we figured out for some difficult games in which the standard parameters give bad results. To detect a game we generate a String of all Objects (npc, movable, immovable, ect...) and store the Hash value of this String. All the hashes from the known games are stored, in a running Game we generate another String of these Objects and compare the generated hash value to the stored ones. 